---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 300,
  message=FALSE,
  warning=FALSE
)
```

[![Travis build status](https://travis-ci.org/italocegatta/fipe.svg?branch=master)](https://travis-ci.org/italocegatta/fipe)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/italocegatta/fipe?branch=master&svg=true)](https://ci.appveyor.com/project/italocegatta/fipe)
[![CRAN_Release_Badge](http://www.r-pkg.org/badges/version-ago/fipe)](https://CRAN.R-project.org/package=fipe)

# fipe

`fipe` is a R package to access [Fipe](https://veiculos.fipe.org.br)'s average prices of vehicles on the Brazilian national market. The prices effectively used in negotiations vary according to region, vehicle's conservation, color, accessories or any other factor that might influence the conditions of demand and supply for a specific vehicle. The year of the vehicle refers to the year of the model and are not considered vehicles for professional or special use. The values are expressed in R$ (reais) of the month/year of reference.

## Installation

You can install the development version from github:

```{r eval=FALSE}
# install.packages('devtools')
devtools::install_github('italocegatta/fipe')
```

The stable version is availabe on [CRAN](https://CRAN.R-project.org)

```{r eval=FALSE}
install.packages("fipe")
```

## Example

The function `fipe_vehicle` provide acces to historial data of brazilian cars 

```{r example}
library(fipe)
library(ggplot2)
library(dplyr)

bmw_x6  <- fipe_vehicle(
  model = "x6 ", 
  make = "bmw", 
  year = c(0, 2017:2015),
  date = seq.Date(as.Date("2013-01-01"), as.Date("2017-12-01"), by = "4 months")
)

bmw_x6 
```


```{r plot_history, fig.width=8, fig.height=6}
bmw_x6 %>%
  ggplot(aes(date, price, color = year, group = year)) +
    geom_line(color = "grey30") +
    geom_point(size = 3) +
    facet_wrap(~model) +
    labs(
      x = "Referance date",
      y = "Price (R$)",
      color = "Year"
    ) +
    scale_y_continuous(breaks = seq(0, 700000, 50000), labels = scales::number) +
    scale_x_date(date_breaks = "1 year", date_labels = "%b/%y") +
    scale_color_viridis_d() +
    theme_bw() +
    theme(legend.position = "top") 
```

```{r plot_compare, fig.width=8, fig.height=6}
bmw_x6 %>% 
  filter(date == max(date)) %>% 
  mutate(model = reorder(model, price, max)) %>% 
    ggplot(aes(price, model)) +
    geom_line(aes(group = model), color = "cadetblue4", size = 2) +
    geom_point(size = 10, color = "cadetblue4") +
    geom_text(aes(label = year), color = "white", size = 3) +
    labs(
      x = "Price (R$)",
      y = "Model"
    ) +
    scale_x_continuous(breaks = seq(0, 700000, 50000), labels = scales::number) +
    theme_bw()
```

